\Title

### 2015-11-02 manuscript.tex
Better bibtex entries for software
Had to tweak where the url fields would go to show on the reference
list. Kind of hacky but works.
Cite software packages

\todo{Cite packages in the references.txt file.}
\todo{Check which conjugate gradient scipy.space.linalg.solve uses.}

@@

>>>>

The implementation relies on the open-source libraries
scipy and numpy \citep[][ \url{http://scipy.org}]{jones2001}
for array-based computations,
matplotlib \citep[][ \url{http://matplotlib.org}]{hunter2007}
and seaborn
\citep[][ \url{http://stanford.edu/~mwaskom/software/seaborn}]{waskom2015}
for plots and maps,
and Fatiando a Terra \citep[][ \url{http://www.fatiando.org}]{uieda2013}
for geophysics specific tasks (e.g., forward modeling).

The computational experiments
(e.g., data processing, synthetic tests, real data application)
were performed in
Jupyter (formerly IPython) notebooks
\citep[][ \url{http://jupyter.org/}]{perez2007}.

\todo{Check which conjugate gradient scipy uses}

@@

The authors are indebted to the developers and maintainers of the open-source
software without which this work would not have been possible.
